\Large \bf 6.824 Final Project

### 2014-05-12 writeup/paper.tex
add section about server config

>>>>

\subsection{Server Configuration}

Two Amazon AWS clusters were provisioned to test real-life performance of the system. The faster of the clusters used Amazon's m3.large instance type, where each server has 7.5 gigabytes of RAM, 2 Intel Xeon i5 Sandy Bridge CPU cores, and 1 32 gigabyte solid state drive. Real-world network performance, measured using iperf, was approximately 700 Mb/s. The slower of the clusters used Amazon's m1.small instance type, where each server has 1.7 gigabytes of RAM, 1 Intel Xeon Westmere core, and 1 160 gigabyte hard disk drive. Real-world network performance was approximately 150 Mb/s. Each cluster had one control node and twelve slave nodes. Instances were allocated on multi-tenant hardware, and nodes within a cluster were within the same region and availability zone.
